MCC Predictions

### 2018-04-20 models/predictions.Rmd
results from ex3

---
title: "MCC Predictions"
author: "Manuel Bohn"
date: "9 4 2018"
output: word_document
---

@@

@@

pred %>%
  knitr::kable(digits = 3)

ggplot(pred, 
       aes(x = Model, y = corr, fill = Model)) +
  geom_bar(stat="identity") + 
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x=" ",y="Proportion Choosing More Informative")+
  facet_grid(Experiment ~ Change*Alignment)+
  theme_few(base_size = 12) + 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank(),axis.title.x=element_blank())+
  ylim(0,1)

@@

>>>>

---
title: "MCC Predictions"
author: "Manuel Bohn"
date: "9 4 2018"
output: html_document
---

@@

```{r data}

@@

@@

```{r plot}
#pred %>%
#  knitr::kable(digits = 3)

ggplot(pred, 
       aes(x = Change, y = corr, fill = Model)) +
  geom_bar(stat="identity",position = position_dodge()) + 
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x=" ",y="Proportion Choosing More Informative")+
  facet_grid(Experiment ~ Alignment)+
  theme_few(base_size = 12) + 
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  ylim(0,1)
```

```{r MH}
# MH?
ggplot(pred, 
       aes(x = Change, y = corr, fill = Alignment)) +
  geom_bar(stat="identity", position = position_dodge(), color = 'black') + 
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x=" ",y="Proportion Choosing More Informative")+
  facet_grid(Experiment ~ Model)+
  theme_few(base_size = 12) + 
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  ylim(0,1)
```
